Variation in Primary Care Prescribing in Wales due to COVID-19

### 2021-09-09 writing/paper.Rmd

---
title             : "Variation in Primary Care Prescribing in Wales due to COVID-19"
shorttitle        : "Welsh Primary Care COVID Prescribing"

author: 
  - name          : "Will Hardy"
    affiliation   : "1,2"
    corresponding : yes    # Define only one corresponding author
    address       : "Postal address"
    email         : "my@email.com"
  - name          : "Susan Murphy"
    affiliation   : "3"
  - name          : "Dyfrig Hughes"
    affiliation   : "1"
  - name          : "Daniel Hill-McManus"
    affiliation   : "1"

affiliation:
  - id            : "1"
    institution   : "Centre for Health Economics & Medicines Evaluation, Bangor University, LL55 2PZ"
  - id            : "2"
    institution   : "Institute for the Psychology of Elite Performance, Bangor University, LL55 2PZ"
  - id            : "3"
    institution   : "Betsi Cadwaladr University Health Board"

keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "../references/library.bib"]

header-includes:
   - \usepackage{caption}
csl               : "../references/apa.csl"
always_allow_html : true
output            : 
  - html_document

---

```{r setup, include = FALSE}
## Packages
# devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(rstan) # needed to load prophet
library(prophet)
library(fable)
library(fable.prophet)
library(fasster)
library(feasts)
library(furrr)
library(rebus)
library(serCymruTools)
library(knitr)
library(kableExtra)
library(geepack)
library(papaja)

@@

## Data
gp <- 
  read_rds("../data/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as.character(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

@@

differences <- 
  map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
  mutate(drug = case_when(drug == "contra" ~ "oral",
                          !drug == "contra" ~ drug),
         drug = relevel(as_factor(drug), ref = "all_drugs"),
         sd = sd^.25) # Error in serCymruTools when calculated

# GP extract data
data_files <-
  paste0("../data/prescribing_data/", list.files("../data/prescribing_data")) 
names(data_files) <- 
  str_remove_all(list.files("../data/prescribing_data"), ".rds")

gp_extract <- 
  map_dfr(.x = data_files,
          .f = ~(read_rds(.x) %>% 
            filter(practice_id %in% unique(differences$regional_unit))),
          .id = "drug") 
```

```{r, analysis-preferences}
# Seed for random number generation
set.seed(32)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = TRUE)
kable_opts <- options(knitr.kable.NA = "-")
```

@@

```{r, table-2}
read_rds("../data/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as.character(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>%  
  filter(year == 2020) %>% 
  select(npat, ngp, dispensing, wimd2019:flu) %>% 
  mutate(across(p_male:flu, ~.x*100)) %>% 
  psych::describe() %>% 
  select(mean, sd, median, min, max) %>% 
  kable(digits = 2)
```

@@

```{r, figure-2, fig.cap="Distribution of the difference between observed and forecast prescribing, expressed as a percentage of forecast prescribing. Grey line marks forecast level of prescribing. Pink shading covers duration of Wales' \"stay at home\" order. Please note the difference y-axis scales across the plots.", dpi=450}
differences_quantiles <- 
  differences %>% 
  na.omit() %>% 
  group_by(datename, drug) %>% 
  summarise(mean_prop = mean(prop, na.rm = T),
            med_prop = median(prop, na.rm = T),
            sd_prop = sd(prop, na.rm = T),
            se_prop = sd(prop, na.rm = T)/sqrt(length(prop)),
            enframe(quantile(prop, seq(.1,.9,.2)), 
                    "Percentile", "prop"),
            .groups = "drop") %>% 
  mutate(datename = month(datename),
         prop = 100*(prop - 1)) # Percentage change instead of proportion

differences_quantiles %>%
  mutate(datename = factor(x = datename, levels = 1:8, 
                           labels = month.abb[1:8])) %>% 
  mutate(drug = case_when(drug == "all_drugs" ~ "All",
                          drug == "ace" ~ "ACE inhibitors",
                          drug == "adreno" ~ "Adrenoceptor agonists",
                          drug == "azithro" ~ "Azithromycin",
                          drug == "contra" ~ "Oral contraceptives",
                          drug == "cortico" ~ "Corticosteroids",
                          drug == "hcq" ~ "Hydroxycholoroquine",
                          drug == "nsaid" ~ "NSAIDs",
                          drug == "paracet" ~ "Paracetamol",
                          drug == "ssri" ~ "SSRIs",
                          drug == "vitd" ~ "Vitamin D",
                          drug == "warfarin" ~ "Warfarin"),
         drug = relevel(as_factor(drug), ref = "All")) %>%
  ggplot(aes(x = datename, col = drug, 
             group = Percentile)) +
  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
            fill = 'pink', col = 0,alpha = 0.03) +
  geom_line(aes(y = prop, lty = Percentile)) +
  geom_hline(aes(yintercept = 0), alpha = .5) +
  facet_wrap(~drug, scales = "free") + 
  guides(size = "legend", colour = "none") + 
  theme(legend.position = "bottom", text = element_text(size = 10)) +
  scale_linetype_manual(breaks = c("10%", "30%", "50%"), # Remove 70% and 90% from legend
                        values = c(3,2,1,2,3), # Replicate line type
                        labels = c("10% lower; 90% upper", # Amalgamate line type labels
                                   "30% lower; 70% uppper", "50%")) +
  xlab("Month") +
  ylab("Percentage difference from forecast prescribing")

  ggsave(filename = "Draft 2/Figures/Figure 2.png", device = "png",
         width = 10.5)

```
```{r}
differences_quantiles %>%
  mutate(datename = factor(x = datename, levels = 1:8, 
                           labels = month.abb[1:8])) %>% 
  mutate(drug = case_when(drug == "all_drugs" ~ "All",
                          drug == "ace" ~ "ACE inhibitors",
                          drug == "adreno" ~ "Adrenoceptor agonists",
                          drug == "azithro" ~ "Azithromycin",
                          drug == "contra" ~ "Oral contraceptives",
                          drug == "cortico" ~ "Corticosteroids",
                          drug == "hcq" ~ "Hydroxycholoroquine",
                          drug == "nsaid" ~ "NSAIDs",
                          drug == "paracet" ~ "Paracetamol",
                          drug == "ssri" ~ "SSRIs",
                          drug == "vitd" ~ "Vitamin D",
                          drug == "warfarin" ~ "Warfarin"),
         drug = relevel(as_factor(drug), ref = "All")) %>% 
  filter(drug == "Adrenoceptor agonists" & 
           datename == "Mar")

@@

```{python, composite-sd-function-py, eval=FALSE}

from __future__ import print_function, division  # requires python 2.6 or later (2.7 or later preferred)
import math

__all__ = ['iterable', 'avg', 'sample_SD', 'composite_SD']

def iterable(obj):
    '''True iff obj is iterable: a list, tuple, or string.'''
    return hasattr(obj, '__contains__')

def avg(samples):
    if len(samples) >= 1:
        return sum(samples) / len(samples)
    return float('nan')

def sample_SD(samples):
    '''input is an array of samples; result is the standard deviation'''
    mean = avg(samples)
    sum_of_squared_deviations = 0;
    sd = 0
    if len(samples) >= 2:
        for datum in samples:
            sum_of_squared_deviations += ((datum - mean) * (datum - mean));
        sd = math.sqrt(sum_of_squared_deviations / (len(samples)-1) );
    return sd

def composite_SD(means, SDs, ncounts):
    '''Calculate combined standard deviation via ANOVA (ANalysis Of VAriance)
       See:  http://www.burtonsys.com/climate/composite_standard_deviations.html
       Inputs are:
         means, the array of group means
         SDs, the array of group standard deviations
         ncounts, number of samples in each group (can be scalar
                  if all groups have same number of samples)
       Result is the overall standard deviation.
    '''
    G = len(means)  # number of groups
    if G != len(SDs):
        raise Exception('inconsistent list lengths')
    if not iterable(ncounts):
        ncounts = [ncounts] * G  # convert scalar ncounts to array
    elif G != len(ncounts):
        raise Exception('wrong ncounts list length')

    # calculate total number of samples, N, and grand mean, GM
    N = sum(ncounts)  # total number of samples
    if N <= 1:
        raise Exception("Warning: only " + str(N) + " samples, SD is incalculable")
    GM = 0.0
    for i in range(G):
        GM += means[i] * ncounts[i]
    GM /= N  # grand mean

    # calculate Error Sum of Squares
    ESS = 0.0
    for i in range(G):
        ESS += ((SDs[i])**2) * (ncounts[i] - 1)

    # calculate Total Group Sum of Squares
    TGSS = 0.0
    for i in range(G):
        TGSS += ((means[i]-GM)**2) * ncounts[i]

    # calculate standard deviation as square root of grand variance
    result = math.sqrt((ESS+TGSS)/(N-1))
    return result

samples = range(10)
print(samples)
print('avg=', avg(samples))
sd = sample_SD(samples)
print('sd=', sd)
pt1 = [0,1,2]
pt2 = [3,4]
pt3 = [5,6,7,8,9]
means = [avg(pt1), avg(pt2), avg(pt3)]
SDs = [sample_SD(pt1), sample_SD(pt2), sample_SD(pt3)]
ncounts = [len(pt1), len(pt2), len(pt3)]
sd2 = composite_SD(means, SDs, ncounts)
print('sd2=', sd2)

samples = range(9)
print('avg=', avg(samples))
sd = sample_SD(samples)
print('sd=', sd)
pt1 = [0,1,2]
pt2 = [3,4,5]
pt3 = [6,7,8]
means = [avg(pt1), avg(pt2), avg(pt3)]
SDs = [sample_SD(pt1), sample_SD(pt2), sample_SD(pt3)]
ncounts = 3
sd2 = composite_SD(means, SDs, ncounts)
print('sd2=', sd2)
```

```{r, composite-sd-function-r, echo=FALSE}
avg <- function(samples){
  if (length(samples) >= 1){
    return(sum(samples) / length(samples))
  }
  else{return(NaN)}
}

@@

```{r, table-3-single-fcts, eval=FALSE}
nat_data <- 
  data_files %>% 
  map_dfr(read_rds, .id = "drug") %>% 
  group_by(drug, datename) %>% 
  summarise(n = sum(quantity), .groups = "drop")

plan(multisession)
precribing_cv_models <- 
  nat_data %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  as_tsibble(index = "datename", key = "regional_unit") %>% 
  serCymruTools::regionalCV(cv_dist = 8, init = 36, step = 3)
plan(sequential)

precribing_cv_models

@@

plan(cluster)
system.time(prescribing_fcsts <-
                nat_data %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  as_tsibble(index = "datename", key = "regional_unit") %>%
              filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
              regionalJointFcsts())  
plan(sequential)

best_model_discrep <- 
  best_model %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(prescribing_fcsts,
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(mutate(select(                nat_data %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) , 
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - med, # observed - forecast
         prop = n / med) %>% 
  ungroup()

best_model_discrep %>% 
  filter(!datename %in% yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug"))) %>% 
  group_by(regional_unit) %>% 
  summarise(n = sum(n),
            sd = compositeSD(.mean, sd, rep(1, length(sd))),
            .mean = sum(.mean)) %>% 
  mutate(lb = .mean - 1.96*sd,
         ub = .mean + 1.96*sd,
         lb_mean_pct_change = (100 * (n - ub)/ ub),
         mean_pct_change = (100 * (n - .mean)/ .mean),
         ub_mean_pct_change = (100 * (n - lb)/ lb)) %>% 
  select(regional_unit, lb_mean_pct_change, mean_pct_change, ub_mean_pct_change) %>% 
  mutate(pct_change = paste0(printnum(mean_pct_change), 
                             "[", printnum(lb_mean_pct_change), ",", 
                             printnum(ub_mean_pct_change), "]")) %>% 
  select(regional_unit, pct_change)

best_model_discrep %>% 
  mutate(prop = 100*(prop-1)) %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename, values_from = prop) %>% 
  kable(digits = 2)
```

```{r, table-3}
monthly_diffs <- 
  differences %>% 
  select(drug, datename, .mean, sd, n) %>% 
  na.omit() %>% 
  group_by(drug, datename) %>% 
  summarise(n = sum(n),
            sd = compositeSD(.mean, sd, rep(nrow(.),length(.mean))),
            .mean = sum(.mean),
            .groups = "drop") %>% 
  mutate(lb = .mean - 1.96*sd,
         ub = .mean + 1.96*sd,
         lb_mean_pct_change = (100 * (n - ub)/ ub),
         mean_pct_change = (100 * (n - .mean)/ .mean),
         ub_mean_pct_change = (100 * (n - lb)/ lb)) %>% 
  mutate(datename = month(datename),
         pct_change = paste0(printnum(mean_pct_change), 
                             "[", printnum(lb_mean_pct_change), ",", 
                             printnum(ub_mean_pct_change), "]")) %>% 
  pivot_wider(id_cols = drug, names_from = datename, values_from = pct_change)

@@

left_join(lockdown_diffs, monthly_diffs) %>%
  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
        align = "lrrrrrrrrr",
        booktabs = TRUE,
        caption = "Monthly percentage change in prescribing") %>%
  add_header_above(header = c(" " = 1,
                              "Mean percentage change [95% CI]" = 9)) %>%
  landscape()
```

```{r, eval=FALSE}
differences %>% 
  filter(drug == "adreno" &
           datename == yearmonth("2020 Mar")) %>% 
  ggplot(aes(x = prop-1)) +
  geom_histogram() +
  geom_vline(aes(xintercept = mean(prop-1)))

differences %>% 
  select(drug, datename, .mean, sd, n) %>% 
  na.omit() %>% 
  group_by(drug, datename) %>% 
  summarise(n = sum(n),
            sd = compositeSD(.mean, sd, rep(nrow(.),length(.mean))),
            .mean = sum(.mean),
            .groups = "drop") %>% 
  filter(drug == "adreno" &
           datename == yearmonth("2020 Mar"))

differences %>% 
  filter(drug == "adreno" &
           datename == yearmonth("2020 Mar")) %>% 
  summarise(.mean = sum(.mean),
            n = sum(n),
            prop = mean(prop))

differences %>% 
  filter(drug == "adreno" &
           datename == yearmonth("2020 Mar")) %>% 
  mutate(prop_correct = if_else(prop == n/med, TRUE, FALSE))
```

@@

```{r, eval=FALSE}
gp_extract %>% 
  filter(str_detect(datename, "-19")) %>% 
  group_by(drug) %>% 
  summarise(n = sum(quantity)/1e6) %>% 
  left_join(lockdown_diffs %>% 
  select(drug, pct_change), by = "drug")
```

>>>>

---
title: "Variation in Primary Care Prescribing in Wales due to COVID-19"
author:
- name: Will Hardy
  affiliation: '1'
  corresponding: yes
  address: Postal address
  email: my@email.com
- name: Susan Murphy
  affiliation: '3'
- name: Dyfrig Hughes
  affiliation: '1'
- name: Daniel Hill-McManus
  affiliation: '1'
shorttitle: Welsh Primary Care COVID Prescribing
output:
  html_document: default
  pdf_document: default
keywords: keywords
wordcount: X
bibliography:
- r-references.bib
- ../references/library.bib
header-includes: \usepackage{caption}
csl: ../references/apa.csl
always_allow_html: yes
affiliation:
- id: '1'
  institution: Centre for Health Economics & Medicines Evaluation, Bangor University,
    LL55 2PZ
- id: '2'
  institution: Betsi Cadwaladr University Health Board
---

```{r setup, include = FALSE}
## Packages
# devtools::install_github("https://github.com/w-hardy/serCymruTools")
library(tidyverse)
library(lubridate)
library(tsibble)
library(fable)
library(feasts)
library(furrr)
library(rebus)
library(serCymruTools)
library(knitr)
library(kableExtra)
library(geepack)
library(papaja)
library(fuzzyjoin)

@@

plan(cluster)
## Data
gp <- 
  read_rds("../data/gp_agesex_qof_combined.rds") %>% 
  mutate(npat = N,
         N = NULL,
         practice_id = as.character(practiceid)) %>% 
  ungroup() %>% 
  janitor::clean_names() %>% 
  select(practice_id, year, npat)

@@

differences <- 
  furrr::future_map_dfr(.x = differences_files,
          .f = ~read_rds(paste0("../data/differences/", .x)),
          .id = "drug") %>% 
    mutate(.mean = mean(dist),
           drug = relevel(as_factor(drug), ref = "quant_all_drugs"))
plan(sequential)

# GP extract data
data_files <-
  paste0("../data/prescribing_data/", list.files("../data/prescribing_data"))
names(data_files) <-
  str_remove_all(list.files("../data/prescribing_data"), ".rds")
# 
# gp_extract <- 
#   map_dfr(.x = data_files[1:11],
#           .f = ~(read_rds(.x)),
#           .id = "drug")
```

```{r, analysis-preferences}
# Seed for random number generation
set.seed(32)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, cache = FALSE, echo = FALSE)
kable_opts <- options(knitr.kable.NA = "-")
```

@@

```{r, table-2}
tibble(regional_unit = unique(differences$regional_unit)) %>% 
  left_join(read_rds("../data/gp_agesex_qof_combined.rds") %>% 
              mutate(npat = N,
                     N = NULL,
                     regional_unit = as.character(practiceid)) %>% 
              ungroup() %>% 
              janitor::clean_names() %>%  
              filter(year == 2020)) %>% 
  select(npat, ngp, dispensing, wimd2019:flu) %>% 
  mutate(across(p_male:flu, ~.x*100)) %>% 
  tibble() %>% 
  psych::describe(fast = TRUE) %>% 
  kable(digits = 2, caption = "Summary of prescribing data and GP practice characteristics")
```

```{r}
differences %>% 
  dplyr::group_by(drug) %>% 
  dplyr::count() %>% 
  mutate(n = n/8)

monthlyPrescribing <- 
  function(data){
    data %>% 
      janitor::clean_names() %>% 
      mutate(datename = dmy(paste0("28-", datename)),
             practice_id = as.character(practice_id)) %>% 
      countRegional(practice_id, datename, quantity) %>% 
      mutate(year = year(datename)) %>%
      as_tibble() %>% 
      inner_join(gp %>% 
                   select(practice_id, year, npat), 
                 by = c("regional_unit" = "practice_id", "year")) %>% 
      mutate(n = 1000*n/npat,
             datename = yearmonth(datename),
             regional_unit = as_factor(regional_unit)) %>% 
      select(-c(npat, year)) %>% 
      as_tsibble(index = datename, key = regional_unit) %>% 
      fill_gaps()
  }

plan(cluster)
pres_2019 <- 
  data_files[c(1:10)] %>% 
  furrr::future_map(read_rds) %>% 
  furrr::future_map(monthlyPrescribing) %>% 
  furrr::future_map_dfr(as_tibble, .id = "drug") %>% 
  filter(year(datename) == 2019)
plan(sequential)

pres_2019 %>% 
  right_join(differences %>% 
               group_by(regional_unit, drug) %>% 
               count() %>% 
               select(-n)) %>% 
  filter(drug != "warfarin_ddd") %>% 
  bind_rows(read_rds(data_files[12]) %>% 
              mutate(datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
              rename(regional_unit = practice_id,
                     n = quantity) %>% 
              filter(year(datename) == 2019) %>% 
              right_join(differences %>% 
                           filter(drug == "warfarin_ddd") %>% 
                           group_by(regional_unit, drug) %>% 
                           count() %>% 
                           select(-n))) %>% 
  group_by(drug) %>% 
  summarise(mean = mean(n, na.rm = TRUE),
            sd = sd(n, na.rm = TRUE),
            min = min(n, na.rm = TRUE),
            max = max(n, na.rm = TRUE),
            n = length(unique(regional_unit))) %>% 
  select(drug, n, everything()) %>% 
  kable(digits = 2)

warf_2019 <- 
  read_rds(data_files[12]) %>% 
  mutate(datename = yearmonth(dmy(paste0("28-", datename)))) %>% 
  rename(regional_unit = practice_id) %>% 
  filter(year(datename) == 2019) %>% 
  right_join(differences %>% 
               filter(drug == "warfarin_ddd") %>% 
               group_by(regional_unit, drug) %>% 
               count() %>% 
               select(-n)) %>%

@@

```{r, figure-2, fig.cap="Distribution of the difference between observed and forecast prescribing, expressed as a percentage of forecast prescribing. Grey line marks forecast level of prescribing. Pink shading covers duration of Wales' \"stay at home\" order. Please note the difference y-axis scales across the plots.", dpi=450}
differences_quantiles <- 
  differences %>% 
  na.omit() %>% 
  dplyr::group_by(datename, drug) %>% 
  dplyr::summarise(mean_prop = mean(prop, na.rm = T),
            med_prop = median(prop, na.rm = T),
            sd_prop = sd(prop, na.rm = T),
            se_prop = sd(prop, na.rm = T)/sqrt(length(prop)),
            enframe(stats::quantile(prop, seq(.1,.9,.2)), 
                    "Percentile", "prop"),
            .groups = "drop") %>% 
  dplyr::mutate(datename = month(datename),
         prop = 100*(prop - 1)) # Percentage change instead of proportion

differences_quantiles %>%
  dplyr::mutate(datename = factor(x = datename, levels = 1:8, 
                           labels = month.abb[1:8])) %>% 
  dplyr::mutate(drug = case_when(drug == "quant_all_drugs" ~ "All",
                          drug == "ddd_ace" ~ "ACE inhibitors",
                          drug == "ddd_adreno" ~ "Beta2 adrenoceptor agonists",
                          drug == "ddd_cortico" ~ "Corticosteroids",
                          drug == "ddd_hcq" ~ "Hydroxycholoroquine",
                          drug == "ddd_nsaid" ~ "NSAIDs",
                          drug == "ddd_oral_contra" ~ "Oral contraceptives",
                          drug == "ddd_paracet" ~ "Paracetamol",
                          drug == "ddd_ssri" ~ "SSRIs",
                          drug == "ddd_vitd" ~ "Vitamin D",
                          drug == "warfarin" ~ "Warfarin",
                          drug == "warfarin_ddd" ~"Warfarin"),
         drug = relevel(as_factor(drug), ref = "All")
         ) %>%
  ggplot(aes(x = datename, col = drug, 
             group = Percentile)) +
  geom_rect(aes(xmin = "Mar", xmax = "Jul", ymin = -Inf, ymax = Inf),
            fill = 'pink', col = 0,alpha = 0.03) +
  geom_line(aes(y = prop, lty = Percentile)) +
  geom_hline(aes(yintercept = 0), alpha = .5) +
  facet_wrap(~drug, scales = "free") + 
  guides(size = "legend", colour = "none") + 
  theme(legend.position = "bottom", text = element_text(size = 10)) +
  scale_linetype_manual(values = c(3,2,1,2,3),
                        # labels = c("10% lower; 90% upper", # Amalgamate line type labels
                        #            "30% lower; 70% upper", "50%"),
                        # #breaks = NULL
                        ) +
  # scale_linetype_manual(breaks = c("10%", "30%", "50%"), # Remove 70% and 90% from legend
  #                       values = c(3,2,1,2,3), # Replicate line type
  #                       labels = c("10% lower; 90% upper", # Amalgamate line type labels
  #                                   "30% lower; 70% upper", "50%")
  #                       ) +
  xlab("Month") +
  ylab("Percentage difference from forecast prescribing")

ggsave(filename = "Draft 4/Figures/Figure 2.png", device = "png", width = 10.5)
```

@@

```{r, composite-sd-function-r, eval=FALSE}
avg <- function(samples){
  if (length(samples) >= 1){
    return(sum(samples) / length(samples))
  }
  else{return(NaN)}
}

@@

```{r, table-3-single-fcts, eval=TRUE}
plan(cluster)
nat_data <- # Data for all regional units combined
  data_files %>% 
  furrr::future_map_dfr(read_rds, .id = "drug") %>% 
  filter(drug != "warfarin_ddd") %>% 
  dplyr::group_by(drug, datename) %>% 
  dplyr::summarise(n = sum(quantity, na.rm = TRUE), .groups = "drop") %>% 
  mutate(datename = yearmonth(dmy(paste("28", datename, sep = "-"))),
         regional_unit = as.factor(drug)) %>% # Calling drug regional_unit to save rewriting all the code
  as_tsibble(index = "datename", key = "regional_unit") %>% 
  fill_gaps()

precribing_cv_models <- 
  nat_data %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  serCymruTools::regionalCV(cv_dist = 8, init = 36, step = 1)

@@

#### Monthly forecasts ####
prescribing_fcsts <-
  nat_data %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  filter(!regional_unit %in% best_mape_over_50$regional_unit) %>%
  regionalJointFcsts()

lockdown_fcsts <- 
  nat_data %>% 
  filter(datename < yearmonth(dmy("01-01-2020"))) %>% 
  filter(!regional_unit %in% best_mape_over_50$regional_unit) %>% 
  fableModels() %>%
  generate(h = 8, times = 1000) %>%
  as_tibble() %>% 
  filter(!datename %in% 
           yearmonth(c("2020 Jan", "2020 Feb", "2020 Aug", "2020 Sept", "2020 Oct"))) %>% 
  group_by(.model, regional_unit, .rep) %>% 
  dplyr::summarise(.sim = sum(.sim)) %>%
  # Store as a distribution
  dplyr::summarise(total = distributional::dist_sample(list(.sim))) %>% 
  mutate(mean = mean(total),
         lb_95 = stats::quantile(total, .025),
         lb_80 = stats::quantile(total, .1),
         med = median(total),
         ub_80 = stats::quantile(total, .9),
         ub_95 = stats::quantile(total, .975),
         sd = distributional::variance(total)^.5,
         total = NULL)

plan(sequential)

#### Monthly discreps ####
best_model_discrep <- 
  best_model %>% 
  select(.model, regional_unit) %>% 
  inner_join(mutate(prescribing_fcsts, # Select best forecast
                    datename = yearmonth(datename)), 
             by = c(".model", "regional_unit")) %>%
  left_join(dplyr::mutate(dplyr::select(nat_data, #Join observed dispensing data
                          c(regional_unit, datename, n)), 
                   datename = yearmonth(datename)),
            by = c("datename", "regional_unit")) %>% 
  mutate(discrepancy = n - med, # observed - forecast
         prop = n / med) %>% 
  ungroup()

#### Plot ####
best_model_discrep %>% 
  group_by(regional_unit) %>% 
  dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x)) %>% 
  ggplot(aes(x = datename)) +
  geom_line(aes(y = med)) +
  geom_ribbon(aes(ymin = lb_95, ymax = ub_95), alpha = .3) +
  geom_hline(aes(yintercept = 0), col = "red")+
  facet_wrap(~regional_unit, scales = "free")

#### Table ####
monthly_diffs <- 
  best_model_discrep %>% 
  group_by(regional_unit) %>% 
  dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x)) %>% 
  select(datename, regional_unit, lb_95, med, ub_95) %>% 
  mutate(pct_change = paste0(printnum(med), 
                             "[", printnum(ub_95), ",", 
                             printnum(lb_95), "]")) %>% 
  select(datename, regional_unit, pct_change) %>% 
  pivot_wider(id_cols = regional_unit, names_from = datename, values_from = pct_change)

#### Lockdown discreps ####
lockdown_model_discrep <- 
  best_model %>% 
  select(.model, regional_unit) %>% 
  inner_join(lockdown_fcsts,  # Select best forecast
             by = c(".model", "regional_unit")) %>%
  left_join(nat_data %>% 
              filter(datename > yearmonth("2020 Feb") &
                       datename < yearmonth("2020 Aug")) %>% 
              as_tibble() %>% 
              select(-datename) %>% 
              ungroup() %>% 
              dplyr::group_by(regional_unit) %>% 
              dplyr::summarise(n = sum(n)),
            by = "regional_unit") %>% 
  dplyr::mutate(across(lb_95:ub_95, ~ 100*(n-.x)/.x))

#### Table ####
lockdown_diffs <- 
  lockdown_model_discrep %>% 
  mutate(pct_change = paste0(printnum(med), 
                             "[", printnum(ub_95), ",", 
                             printnum(lb_95), "]")) %>% 
  select(regional_unit, lckdwn = pct_change)

#### Joint table ####
lockdown_diffs %>% 
  left_join(monthly_diffs, by = "regional_unit") %>% 
  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
        align = "lrrrrrrrrr",
        booktabs = TRUE,
        caption = "Monthly percentage change in prescribing") %>%
  kable_styling(font_size = 8) %>% 
  add_header_above(header = c(" " = 1,
                              "Mean percentage change [95% CI]" = 9)) %>%
  landscape()
```

```{r, table-3, eval=FALSE}
monthly_diffs <- 
  differences %>%
  select(drug, datename, .mean, sd, n) %>% 
  na.omit() %>% 
  group_by(drug, datename) %>% 
  summarise(n = sum(n),
            sd = compositeSD(.mean, sd, rep(nrow(.),length(.mean))),
            .mean = sum(.mean),
            .groups = "drop") %>% 
  mutate(lb = .mean - 1.96*sd,
         ub = .mean + 1.96*sd,
         lb_mean_pct_change = (100 * (n - ub)/ ub),
         mean_pct_change = (100 * (n - .mean)/ .mean),
         ub_mean_pct_change = (100 * (n - lb)/ lb)) %>% 
  mutate(datename = month(datename),
         pct_change = paste0(printnum(mean_pct_change), 
                             "[", printnum(lb_mean_pct_change), ",", 
                             printnum(ub_mean_pct_change), "]")) %>% 
  pivot_wider(id_cols = drug, names_from = datename, values_from = pct_change)

@@

left_join(lockdown_diffs, monthly_diffs) %>%
  kable(col.names = c("Drug", "Lockdown", month.abb[1:8]),
        align = "lrrrrrrrrr",
        booktabs = TRUE,
        caption = "Monthly percentage change in prescribing") %>%
  kable_styling(font_size = 8) %>% 
  add_header_above(header = c(" " = 1,
                              "Mean percentage change [95% CI]" = 9)) %>%
  landscape()
```

@@

```{r, eval=FALSE}
gp_extract %>% 
  filter(str_detect(datename, "-19")) %>% 
  group_by(drug) %>% 
  summarise(n = sum(quantity, na.rm = TRUE)/1e6) %>% 
  left_join(lockdown_diffs %>% 
  select(drug, pct_change), by = "drug")
```
